\section{Relevant Projects}
\begin{itemize}
\item \textbf{Recommendation System} | \textbf{Python, Collaborative Filtering, ML, XGBoost}\\
 Developed a model which recommends responsive experts on a particular topic using ensemble collaborative filtering. Various other algorithms were explored in the process. Training data was question-expert answer mapping, word tags used in the question and topics describing the expert’s interests. Similarity was measured between questions using the tf-idf, wordtovec of the tags as features. Was featured in the top 20 of the Byte Cup 2016  challenge.

\item \textbf{Smart Personal Assistant (SPA)} | \textbf{Python, C++, Android, Java}\\
 SPA is an assistant bot, which assists users in scheduling daily routine, automatic tracking of events, detection of important messages and smart alarms system which automatically sets alarms with adaptive correction and prediction of users’ sleep pattern. Gathered phone sensors data like gyroscope etc. and used it in a logistic regression model to predict the asleep/awake state of user.

\item \textbf{Enhancing 0 A.D. Gameplay AI} | \textbf{Python, C++, JavaScript}\\
 Helped enhance the crisis situation decision making of an Aegis AI bot by changing the bot’s planning algorithm upon detection of a situation. Situations can be detected by the bot’s performance e.g. when there is a deadlock for resources vs production of new units. Depending on the situation we designed some plans which the bot can execute to help it recover from the situation.

 \item \textbf{Pai-deia} | \href{http://alseambusher.github.io/Paideia}{jashwanth.in/Paideia} | \textbf{Java, C++, Android, Deep Learning}\\
 This is a Deep Learning based android app that uses Tensorflow and detects objects around you though camera and maps it into one of the classes in Imagenet and then pulls more information about what the user is seeing from Wikipedia and Wolfram Alpha. The results are also tweaked based on a learning model that monitors user's activity and shows more relevant content over time.

 % \item \textbf{Jarvis} | \href{http://github.com/alseambusher/jarvis}{github.com/alseambusher/jarvis} | \textbf{Python, opencv, gtk}\\
 % This is a Human Computer Interaction tool in python using which it is possible to control your Linux system using hand gestures. Users can add their own gestures and assign custom actions using a gtk ui. In order to accommodate any gesture defined by the user, I developed a state transition based approach to do so and published a paper at ICACCI- 2013.
 %\href{https://github.com/alseambusher/jarvis}{https://github.com/alseambusher/jarvis}
 %\item \textbf{QuickFoods} \\ This is an innovative app for hotels to manage their orders with ease even in rush hours. It mainly aims at reducting the time taken to complete the order cycle by bridging the gap between waiters and kitchen. This was built in Intuit LABS and received a lot traction from several five star hotels.

 

 

 % \item \textbf{Social Event Detection} | \href{http://github.com/alseambusher/SED}{github.com/alseambusher/SED} | \textbf{Python, Machine Learning}\\
% In this project, I discovered event-related multimedia and organized them in event-specific clusters, within a collection of Web multimedia. The dataset was multimodal – images along with metadata such as location, description and timestamps. SIFT features were extracted from images to represent them numerically. Then we used an easy to obtain supervisory signal and a SVM classifier to perform multimodal clustering to detect social events.

 %\item \textbf{A Real Time Multiplayer Gaming Network Platform as a Service} - As multiplayer games are becoming more and more complex, there is a need of a simpler way for game developers to manage network. I built a network framework in C++ and Python using which issues such as latency, load balancing, bad connectivity etc. can be addressed through a service.\\
 %\textit{Code: github.com/alseambusher/Easy-Multi-Player}
 %\href{https://github.com/alseambusher/Easy-Multi-Player}{https://github.com/alseambusher/Easy-Multi-Player}
\end{itemize}
\vspace{5pt}
